---
title: "viz_part_1"
author: "Gabriela Jackson"
output: 
  github_document

---

```{r setup, echo = FALSE}
library(tidyverse)
library(ggridges)
```

# Section 1
 Code copied from course website. Load NOAA dataset.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

# Scatterplot
Need to define three things: dataset, aesthetic mappings, and geometry. 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) ##blank, need to add geom()

ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```
Scatterplot, but different. Same code but using piping.
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

##Can filter out before ggplot in the same code using piping.

weather_df %>%
  drop_na() %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```
Keep making the same plot but different. Make a plot and save it, then add geom. 

```{r}
weather_scatterplot =
  weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_scatterplot +
  geom_point()
```
Fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point()

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
##Color aesthetic mapping applies only to scatterplot.

#vs.

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth()

##Here color aesthetic mapping applies to everything (plot + smooth). 
```
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) + #transparent points (alpha blending)
  geom_smooth(se = FALSE) #gets rid of error bars

```
maybe make separate panels:

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~name)
 
```

# Seasonal trends


```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE)
 

weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(.~name) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) #rotate x axis labels

```
Hex
```{r}
 weather_df %>% 
 ggplot(aes(x = tmax, y = tmin)) + 
  geom_hex()

```
## Historgrams
```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + #if you do color it is the lines outside 
  geom_histogram() +
  facet_grid(.~name)

```
## Density plot
```{r}

weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = .3)

```
## Box Plot
```{r}

weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name)) +
  geom_boxplot()

```
## Violin Plots
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax, fill = name)) +
  geom_violin()
```
## Ridge Plot (type of density plot)
```{r}
weather_df %>% 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()

```
## Saving and embedding plots

```{r}
weather_scatterplot = 
  weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~name) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

weather_scatterplot


ggsave("results/weather_scatterplot.pdf", weather_scatterplot,
       width = 8, height = 5)
```
embedding plots
```{r, fig.width = 10}
weather_scatterplot
```

