---
title: "viz_part_2"
author: "Gabriela Jackson"
output: 
  github_document

---

```{r setup, echo = FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
```

# Section 1
 Code copied from course website. Load NOAA dataset.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
##Scatterplot but better this time
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    x = "Minimum Daily Temp (C)",
    y = "Maximum Daily Temp (C)", 
    title = "Scatterplot of daily temp extremes",
    caption = "Data come from the rnoaa package"
  ) +
  scale_x_continuous(
    breaks = c(-10, 0, 15),
    labels = c("-10C", "0", "15")
  )
 
  
   #scale_y_continuous(
    #trans = "sqrt")
  
```
Make a new version
```{r}

ggp_weather = weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    x = "Minimum Daily Temp (C)",
    y = "Maximum Daily Temp (C)", 
    title = "Scatterplot of daily temp extremes",
    caption = "Data come from the rnoaa package"
  ) +
  viridis::scale_color_viridis(
    name = "Location",
    discrete = TRUE)
  
```
Can use scale_color_hue instead, but viridis color pallete is better. 

scale_color_hue(
    name = "Location", h = c(100, 300))
  
## Themes
```{r}
ggp_weather +
  theme_bw() #instead of grey background

ggp_weather +
  theme_classic() #gets rid of gridlines

ggp_weather + 
  theme_minimal() + #gridlines but no outline box 
  theme(legend.position = "bottom") #if you switch the order, theme minimal will override the legend position

```
## Setting options (as first code chunk)

library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

## Data in geom()

```{r}
central_park_df =
  weather_df %>% 
  filter(name == "CentralPark_NY")

waikiki_df = 
  weather_df %>% 
  filter(name == "Waikiki_HA")

ggplot(waikiki_df, aes(x = date, y = tmax)) +
  geom_point() + 
  geom_line(data = central_park_df) #could add separate dataset that included monthly averages, for example

```
## Patchwork...
Figure that has multiple panels, each is *fundamentally different*, but side by side (not single ggplot with faceting!)
```{r}

tmax_tmin_plot =
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmin, color = name)) +
  geom_point() +
  theme(legend.position = "none")

prcp_density_plot =
  weather_df %>% 
  filter(prcp > 0) %>% 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density() +
  theme(legend.position = "none")

seasonality_plot =
  weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  theme(legend.position = "none")

#Patchwork package
(tmax_tmin_plot + prcp_density_plot) / seasonality_plot

```
## Data manipulation
R assumes x axis is a factor, automatically changes a character to factor, and then assumes alphabetical ordering, which is why the x axis is automatically in alphabetical order. 

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()

#relevel the name as a factor variable where Waikiki is the first value
weather_df %>% 
  mutate(name = fct_relevel(name, "Waikiki_HA")) %>% 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()

#In order of the value (median) (of tmax in this case)
weather_df %>% 
  mutate(name = fct_reorder(name, tmax)) %>% 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()

```

```{r}
pulse_df =
  haven::read_sas("data/public_pulse_data.sas7bdat") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit",
    values_to = "bdi",
    names_prefix = "bdi_score_"
  ) %>% 
  select(id, visit, everything()) %>% 
  mutate(
    visit = fct_relevel(visit, "bl")
  )

pulse_df %>% 
  ggplot(aes(x = visit, y = bdi)) +
  geom_boxplot()

```


